Stagnating State Funding for Higher Education and its Effect on Faculty at US Universities

### 2023-07-21 text/sections/05-results.tex
add LP estimates in IBHED data (no effects worth mentioning).

Incumbent professors are relatively unaffected by changes in the state funding for their university in the years following their hire.
\autoref{tab:faculty-shock-illinois-rolling} show estimates of a 1\% change in state funding per student on faculty salaries, rate of exiting the Illinois public university system, and rate of promotion.
The estimates are not discernible from zero, so that faculty who are already at the university (incumbent faculty) seem to have no effects of state funding cuts passed on to them.

>>>>

Incumbent professors are relatively unaffected by changes in the state funding for their university in the years following their hire.
\autoref{tab:faculty-shock-illinois-rolling} show estimates of a 1\% change in state funding per student on faculty salaries, rate of exiting the Illinois public university system, and rate of promotion.
The estimates are not discernible from zero, so that faculty who are already at the university (incumbent faculty) seem to have no effects of state funding cuts passed on to them, in the year of the funding cut.
In the years following, Illinois professors' salaries are not affected by state funding cuts.
Lecturers on the other hand, see a 0.75\% increase in salary in the second and third year after a 10\% increase in state funding (\autoref{fig:salaries-illinois-lp-rolling}), reflecting how lecturers are again more affected changes in public university finances.
Similarly, promotion rate and exit rate among incumbent faculty  (from the Illinois public university system) are unaffected in the years after an initial funding shock (\autoref{fig:promotion-illinois-lp-rolling}, \ref{fig:exit-illinois-lp-rolling}).

### 2023-07-21 text/sections/09-figures-tables.tex
add LP estimates in IBHED data (no effects worth mentioning).

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{Local Projection Estimates for Professor Count per Student, by Professor Group.}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Lecturers.}
        \includegraphics[width=\textwidth]{figures/lecturer-count-lp.png}
        \label{fig:lecturer-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Assistant Professors.}
        \includegraphics[width=\textwidth]{figures/assistant-count-lp.png}
        \label{fig:assistant-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Full Professors.}
        \includegraphics[width=\textwidth]{figures/full-count-lp.png}
        \label{fig:full-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{All Professors.}
        \includegraphics[width=\textwidth]{figures/all-count-lp.png}
        \label{fig:all-count-lp}
    \end{subfigure}
    \label{fig:count-lp}
    \justify
    \footnotesize
    \textbf{Note}:
    These figures show the local projections estimates of regression specification \eqref{eqn:secondstage}, with the funding shock as an instrument for state funding, using IPEDS data.
    The coefficient estimate is effect of state funding ($X_{i,t}$) on faculty count per student ($Y_{i,t}$), while accounting for auto-correlation between different time periods --- i.e., between $X_{i,t}, X_{i,t-1}$ and $Y_{i,t}, Y_{i,t-1}$.
    These results use a $\log-\log$ specification, so the estimates are for the elasticity of professor count per student in a year $t+k$ with respect to state funding in year $t$, where years $k = 0, \hdots, 10$ are on the x-axis. 
    Standard errors are clustered at the state-year level.
\end{figure}

>>>>

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{Local Projection Estimates for Effect of State Funding on Faculty Count per Student at Universities, by Professor Group.}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Lecturers.}
        \includegraphics[width=\textwidth]{figures/lecturer-count-lp.png}
        \label{fig:lecturer-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Assistant Professors.}
        \includegraphics[width=\textwidth]{figures/assistant-count-lp.png}
        \label{fig:assistant-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Full Professors.}
        \includegraphics[width=\textwidth]{figures/full-count-lp.png}
        \label{fig:full-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{All Professors.}
        \includegraphics[width=\textwidth]{figures/all-count-lp.png}
        \label{fig:all-count-lp}
    \end{subfigure}
    \label{fig:count-lp}
    \justify
    \footnotesize
    \textbf{Note}:
    These figures show the local projections estimates of regression specification \eqref{eqn:secondstage}, with the funding shock as an instrument for state funding
    The unit of analysis is the university, and uses IPEDS data.
    The coefficient estimate is effect of state funding ($X_{i,t}$) on faculty count per student ($Y_{i,t}$), while accounting for auto-correlation between different time periods --- i.e., between $X_{i,t}, X_{i,t-1}$ and $Y_{i,t}, Y_{i,t-1}$.
    These results use a $\log-\log$ specification, so the estimates are for the elasticity of professor count per student in a year $t+k$ with respect to state funding in year $t$, where years $k = 0, \hdots, 10$ are on the x-axis. 
    Standard errors are clustered at the state-year level.
\end{figure}

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{Local Projection Estimates for Effect of State Funding on Faculty Salaries per Student at Illinois Public Universities, by Professor Group.}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Lecturers.}
        \includegraphics[width=\textwidth]{figures/salaries-lecturer-illinois-lp-rolling.png}
        \label{fig:salaries-lecturer-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Assistant Professors.}
        \includegraphics[width=\textwidth]{figures/salaries-assistant-illinois-lp-rolling.png}
        \label{fig:salaries-assistant-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Full Professors.}
        \includegraphics[width=\textwidth]{figures/salaries-full-illinois-lp-rolling.png}
        \label{fig:salaries-full-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Administrator Professors.}
        \includegraphics[width=\textwidth]{figures/salaries-administrator-illinois-lp-rolling.png}
        \label{fig:salaries-administrator-illinois-lp-rolling}
    \end{subfigure}
    \label{fig:salaries-illinois-lp-rolling}
    \justify
    \footnotesize
    \textbf{Note}:
    These figures show the local projections estimates of regression specification \eqref{eqn:secondstage}, with the funding shock as an instrument for state funding.
    The unit of analysis is an individual faculty member (at an Illinois public university); funding data come from IPEDS, and faculty salaries from IBHED.
    The coefficient estimate is effect of state funding ($X_{i(j),t}$) on faculty salaries ($Y_{j,t}$), while accounting for auto-correlation between different time periods --- i.e., between $X_{i(j),t}, X_{i(j),t-1}$ and $Y_{i(j),t}, Y_{i(j),t-1}$.
    These results use a $\log-\log$ specification, so the estimates are for the elasticity of faculty salaries student in a year $t+k$ with respect to state funding in year $t$, where years $k = 0, \hdots, 4$ are on the x-axis. 
    Standard errors are clustered at the university-year level.
\end{figure}

### 2023-07-21 text/sections/10-appendix.tex
add LP estimates in IBHED data (no effects worth mentioning).

>>>>

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{Local Projection Estimates for Effect of State Funding on Faculty Promotion Rate at Illinois Public Universities, by Professor Group.}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Lecturers.}
        \includegraphics[width=\textwidth]{figures/promotion-lecturer-illinois-lp-rolling.png}
        \label{fig:promotion-lecturer-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Assistant Professors.}
        \includegraphics[width=\textwidth]{figures/promotion-assistant-illinois-lp-rolling.png}
        \label{fig:promotion-assistant-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Full Professors.}
        \includegraphics[width=\textwidth]{figures/promotion-full-illinois-lp-rolling.png}
        \label{fig:promotion-full-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Administrator Professors.}
        \includegraphics[width=\textwidth]{figures/promotion-administrator-illinois-lp-rolling.png}
        \label{fig:promotion-administrator-illinois-lp-rolling}
    \end{subfigure}
    \label{fig:promotion-illinois-lp-rolling}
    \justify
    \footnotesize
    \textbf{Note}:
    These figures show the local projections estimates of regression specification \eqref{eqn:secondstage}, with the funding shock as an instrument for state funding.
    The unit of analysis is an individual faculty member (at an Illinois public university); funding data come from IPEDS, and faculty promotion rate from IBHED.
    The coefficient estimate is effect of state funding ($X_{i(j),t}$) on faculty promotion rate ($Y_{j,t}$), while accounting for auto-correlation between different time periods --- i.e., between $X_{i(j),t}, X_{i(j),t-1}$ and $Y_{i(j),t}, Y_{i(j),t-1}$.
    These results use a rate$-\log$ specification, so the estimates are for the rate of promotion in a year $t+k$ affected by a 1\% change in state funding in year $t$, where years $k = 0, \hdots, 4$ are on the x-axis. 
    Standard errors are clustered at the university-year level.
\end{figure}

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{Local Projection Estimates for Effect of State Funding on Faculty Exit Rate at Illinois Public Universities, by Professor Group.}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Lecturers.}
        \includegraphics[width=\textwidth]{figures/exit-lecturer-illinois-lp-rolling.png}
        \label{fig:exit-lecturer-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Assistant Professors.}
        \includegraphics[width=\textwidth]{figures/exit-assistant-illinois-lp-rolling.png}
        \label{fig:exit-assistant-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Full Professors.}
        \includegraphics[width=\textwidth]{figures/exit-full-illinois-lp-rolling.png}
        \label{fig:exit-full-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Administrator Professors.}
        \includegraphics[width=\textwidth]{figures/exit-administrator-illinois-lp-rolling.png}
        \label{fig:exit-administrator-illinois-lp-rolling}
    \end{subfigure}
    \label{fig:exit-illinois-lp-rolling}
    \justify
    \footnotesize
    \textbf{Note}:
    These figures show the local projections estimates of regression specification \eqref{eqn:secondstage}, with the funding shock as an instrument for state funding.
    The unit of analysis is an individual faculty member (at an Illinois public university); funding data come from IPEDS, and faculty promotion rate from IBHED.
    The coefficient estimate is effect of state funding ($X_{i(j),t}$) on faculty promotion rate ($Y_{j,t}$), while accounting for auto-correlation between different time periods --- i.e., between $X_{i(j),t}, X_{i(j),t-1}$ and $Y_{i(j),t}, Y_{i(j),t-1}$.
    These results use a rate$-\log$ specification, so the estimates are for the rate of promotion in a year $t+k$ affected by a 1\% change in state funding in year $t$, where years $k = 0, \hdots, 4$ are on the x-axis. 
    Standard errors are clustered at the university-year level.
\end{figure}
